---
title: "Congressional Polling & Women Voters"
output: html_document
date: "`r format(Sys.Date(), '%m/ %d/ %y')`" 
--- 

<br>
Women voters are important and more important to Democrats winning. 

Using __Echelon Insights, Fox News Poll and Monmouth University Poll__, I looked at the generic ballot beginning from Jan 2022 and compared the two party support. 

The Republicans led the generic poll from Jan to June because they averaged over 40% support from women. 

The support fell in July and August to a low of 38%. Democrats support from women maintained throughout the year hovering between 47% and at it’s highest 51%. 

The supreme court ruling on abortion may have had a negative effect on republicans women support.

Democrats took their first lead in July by **0.5%** and have extended the lead to ***3%*** thanks to strong women support.

---------------------------------------------------------


```{r setup, include=FALSE}
library(dygraphs)
library(flexdashboard)  
library(readxl)
library(ggplot2)
library(plotly)
library(knitr)
library(plyr)
library(scales) 
library(lubridate) 
library(dplyr)
```
```{r, echo=FALSE}
genericbal<-read_excel(("~/Documents/RSTUDIO/kaejames.github.io/Gender2022.xlsx"), sheet = "AVG")
knitr::opts_chunk$set(error = TRUE)
```

 
```{r,out.width='100%', echo=FALSE}
p<-ggplot(genericbal)+
  geom_line(aes(x=Date, y=Congress,colour=Party, group=Party), lwd=2) +
  labs(x="", y="", title = "Congressional Midterms 2022",
       caption = "source;Echelon Insights, Fox News Poll & Monmouth University")+
  scale_color_manual(values =c("deepskyblue","indianred2")) +
  theme(plot.title = element_text(color = "black", family = "Ubuntu",  size = 17, face="bold", hjust = 0),
        plot.caption = element_text(color = "black", size=13, face = "italic", family = "Ubuntu"),
        legend.text = element_text(face = "bold"),axis.title.x = element_text(family = 'Ubuntu', face = 'bold'),
        axis.text.x = element_text(face = 'bold', angle = 0, hjust = 0.5),axis.text.y = element_text(face = "bold"),
        plot.subtitle = element_text(color = "black",family="Ubuntu", size = 13))
  
ggplotly(p, tooltip =c("Congress", "Date"))  
``` 

-------------------------------------------------------

```{r,out.width='100%', echo=FALSE}
W<-ggplot(genericbal)+
  geom_line(aes(x=Date, y=Women,colour=Party, group=Party), lwd=2) +
  labs(x="", y="", title = "Who do women support for Congress?",
       caption = "source;Echelon Insights, Fox News Poll & Monmouth University")+
  scale_color_manual(values =c("deepskyblue","indianred2")) +
  theme(plot.title = element_text(color = "black", family = "Ubuntu",  size = 17, face="bold", hjust = 0),
        plot.caption = element_text(color = "black", size=13, face = "italic", family = "Ubuntu"),
        legend.text = element_text(face = "bold"),axis.title.x = element_text(family = 'Ubuntu', face = 'bold'),
        axis.text.x = element_text(face = 'bold', angle = 0, hjust = 0.5),axis.text.y = element_text(face = "bold"),
        plot.subtitle = element_text(color = "black",family="Ubuntu", size = 13))
ggplotly(W, tooltip = c("Women", "Date"))  
``` 
