---
title: "Congressional Polling & Women Voters"
output: html_document
date: "`r format(Sys.Date(), '%m/ %d/ %y')`" 
--- 

<br>

Polling average of generic ballot and women voters for the 2022 midterms elections using __Echelon Insights, Fox News Poll, NYT/Siena, Cygnal,Selzer&Co and Monmouth University Poll__. Recent and fresh polls are average daily whenever posible. There is daily and monthly tracking to see how it compares for both generic ballot and women voters.  

<br>



---------------------------------------------------------


```{r setup, include=FALSE}
library(dygraphs)
library(flexdashboard)  
library(readxl)
library(ggplot2)
library(plotly)
library(knitr)
library(plyr)
library(scales) 
library(lubridate) 
library(dplyr)
```

```{r, echo=FALSE}
genericbal<-read_excel(("~/Documents/RSTUDIO/kaejames.github.io/midterms22.xlsx"), sheet = "daily") 
knitr::opts_chunk$set(error = TRUE)
```
```{r, echo=FALSE}
monthly<-read_excel(("~/Documents/RSTUDIO/kaejames.github.io/midterms22.xlsx"), sheet = "month") 
knitr::opts_chunk$set(error = TRUE)
```
```{r, echo=FALSE}
foxnews<-read_excel(("~/Documents/RSTUDIO/kaejames.github.io/foxnews.xlsx"), sheet = "Avg") 
knitr::opts_chunk$set(error = TRUE)
```

 
```{r,out.width='100%', echo=FALSE}
p<-ggplot(genericbal)+
  geom_line(aes(x=Date, y=Ballot,colour=Party, group=Party), lwd=2) +
  labs(x="", y="", title = "Who is leading? - Daily Tracking",
       caption = "source;Echelon Insights, Fox News Poll & Monmouth University")+
  scale_color_manual(values =c("deepskyblue","indianred2")) +
  theme(plot.title = element_text(color = "black", family = "Ubuntu",  size = 17, face="bold", hjust = 0),
        plot.caption = element_text(color = "black", size=13, face = "italic", family = "Ubuntu"),
        legend.text = element_text(face = "bold"),axis.title.x = element_text(family = 'Ubuntu', face = 'bold'),
        axis.text.x = element_text(face = 'bold', angle = 0, hjust = 0.5),axis.text.y = element_text(face = "bold"),
        plot.subtitle = element_text(color = "black",family="Ubuntu", size = 13)) +
  scale_y_continuous(limits = c(35,55))
  
ggplotly(p, tooltip =c("Ballot", "Date"))  
``` 

-------------------------------------------------------
<left>Women voters are important and more important to Democrats winning, they will need a double digit edge against the Republicans in November to win.</left>

<br>

```{r,out.width='100%', echo=FALSE}
W<-ggplot(genericbal)+
  geom_line(aes(x=Date, y=Women,colour=Party, group=Party), lwd=2) +
  labs(x="", y="", title = "Women support for Congress? - Daily Tracking",
       caption = "source;Echelon Insights, Fox News Poll & Monmouth University")+
  scale_color_manual(values =c("deepskyblue","indianred2")) +
  theme(plot.title = element_text(color = "black", family = "Ubuntu",  size = 17, face="bold", hjust = 0),
        plot.caption = element_text(color = "black", size=13, face = "italic", family = "Ubuntu"),
        legend.text = element_text(face = "bold"),axis.title.x = element_text(family = 'Ubuntu', face = 'bold'),
        axis.text.x = element_text(face = 'bold', angle = 0, hjust = 0.5),axis.text.y = element_text(face = "bold"),
        plot.subtitle = element_text(color = "black",family="Ubuntu", size = 13))+
   scale_y_continuous(limits = c(35,55))
ggplotly(W, tooltip = c("Women", "Date"))  
``` 
<br>

<left>Monthly Polling Aggregate that shows a different picture for both party and women voters.It shows republicans peaked at their highest in May until the end of June.</left> 
 
<br> 
 
```{r,out.width='100%', echo=FALSE}
p<-ggplot(monthly)+
  geom_line(aes(x=Date, y=Congress,colour=Party, group=Party), lwd=2) +
  labs(x="", y="", title = "Who is leading? - Monthly Tracking",
       caption = "source;Echelon Insights, Fox News Poll & Monmouth University")+
  scale_color_manual(values =c("deepskyblue","indianred2")) +
  theme(plot.title = element_text(color = "black", family = "Ubuntu",  size = 17, face="bold", hjust = 0),
        plot.caption = element_text(color = "black", size=13, face = "italic", family = "Ubuntu"),
        legend.text = element_text(face = "bold"),axis.title.x = element_text(family = 'Ubuntu', face = 'bold'),
        axis.text.x = element_text(face = 'bold', angle = 0, hjust = 0.5),axis.text.y = element_text(face = "bold"),
        plot.subtitle = element_text(color = "black",family="Ubuntu", size = 13)) +
  scale_y_continuous(limits = c(35,55))
  
ggplotly(p, tooltip =c("Congress", "Date"))  
``` 

```{r,out.width='100%', echo=FALSE}
p<-ggplot(monthly)+
  geom_line(aes(x=Date, y=Women,colour=Party, group=Party), lwd=2) +
  labs(x="", y="", title = "Women support for Congress? - Monthly Tracking",
       caption = "source;Echelon Insights, Fox News Poll & Monmouth University")+
  scale_color_manual(values =c("deepskyblue","indianred2")) +
  theme(plot.title = element_text(color = "black", family = "Ubuntu",  size = 17, face="bold", hjust = 0),
        plot.caption = element_text(color = "black", size=13, face = "italic", family = "Ubuntu"),
        legend.text = element_text(face = "bold"),axis.title.x = element_text(family = 'Ubuntu', face = 'bold'),
        axis.text.x = element_text(face = 'bold', angle = 0, hjust = 0.5),axis.text.y = element_text(face = "bold"),
        plot.subtitle = element_text(color = "black",family="Ubuntu", size = 13)) +
  scale_y_continuous(limits = c(35,55))
  
ggplotly(p, tooltip =c("Women", "Date"))  
``` 

```{r,out.width='100%', echo=FALSE}
p<-ggplot(foxnews)+
  geom_line(aes(x=Date, y=Results,colour=Party, group=Party), lwd=2) +
  labs(x="", y="", title = "Fox News Polls & Results",
       caption = "source;Echelon Insights, Fox News Poll & Monmouth University")+
  scale_color_manual(values =c("deepskyblue","indianred2")) +
  theme(plot.title = element_text(color = "black", family = "Ubuntu",  size = 17, face="bold", hjust = 0),
        plot.caption = element_text(color = "black", size=13, face = "italic", family = "Ubuntu"),
        legend.text = element_text(face = "bold"),axis.title.x = element_text(family = 'Ubuntu', face = 'bold'),
        axis.text.x = element_text(face = 'bold', angle = 0, hjust = 0.5),axis.text.y = element_text(face = "bold"),
        plot.subtitle = element_text(color = "black",family="Ubuntu", size = 13)) +
  scale_y_continuous(limits = c(35,55))
  
ggplotly(p, tooltip =c("Results", "Date")) 
```